Final Project Paper

### 2017-03-07 paper/paper.Rmd
added future work

>>>>

While we looked at GDP and crime rate, to extend the work we have done here, other researchers can also compare GDP and crime rate per city with other covariates that may also affect these two. One example is other related work looks at economic uncertainty as a covariate and there are other covariates that could possibly show a correlation between the GDP and crime rate of a city such as education, population density, health metrics, and many more.

One other aspect to consider is the particular datasets used and how the data is measured. Since we are doing by city, crime rate to us is defined as total number of crimes divided by the population of each city or metropolitan area within the dataset. The GDP dataset that we chose to use was in a very unfortunate format when trying to combine it with the crime dataset, so I would suggest that in future work an alternative GDP dataset is used that is by actual city in the US rather than metropolitan area.
